An improved metric for the analysis of swarms

### 2017-10-12 paper.tex
Introduction added

%\section{Introduction\label{methods:SwarmStability}}
\emph{Swarming} in the animal kingdom of ants, bees, fish and birds for instance has long been studied by scientists. From these studies mathematical models and algorithms have evolved. The models and algorithms have in turn captured the interest of computing scientists who are interested in applying them to large groups of autonomous mobile \emph{agents} (`robots'). The cooperative coordination of these agents can take many forms such as following a set path~\cite{HCS:09}, existing in a static space~\cite{EP:10, GP:02, GP:04} or foraging as a colony~\cite{HER:11, GK:07}. One of the attributes of swarms that has captured the interest of scientists is that the models and algorithms used to coordinate them are generally sets of simple rules. These simple rules cause the agents to appear to work cooperatively. These rules can also generate movement that does not support the goal of the swarm but and is a direct result of the agents moving towards optimum positions within the swam structure. This internal movement can be identified by analysing the changes in the inter-agent interactions. This paper discusses two metrics that differ in their approach to identify the changes. The distance metric uses variations in the inter-agent spaces, as used by Navarro et al.~\cite{NIM:09}. The new metric uses the generated magnitudes from an agents' \textit{inter-agent vectors} that are induced by an agents' field effects.

Both metrics allow a comparison of the effects of different swarming algorithms on a swarm's structure.
This paper presents a swarm model and then applies the two metrics to this model to present a comparison of the two metrics and also to use the new metric to highlight a swarms `state'.

>>>>

%\section{Introduction\label{methods:SwarmStability}}
\emph{Swarming} in the animal kingdom of ants, bees, fish and birds for instance has long been studied by scientists. From these studies mathematical models and algorithms have evolved. The models and algorithms have in turn captured the interest of computing scientists who are interested in applying them to large groups of autonomous mobile \emph{agents} (`robots'). The cooperative coordination of these agents can take many forms such as following a set path~\cite{HCS:09}, existing in a static space~\cite{EP:10, GP:02, GP:04} or foraging as a colony~\cite{HER:11, GK:07}. One of the attributes of swarms that has captured the interest of scientists is that the models and algorithms used to coordinate them are generally sets of simple rules. These simple rules cause the agents to appear to work cooperatively. These rules can also generate movement that does not contribute to the goal of the swarm but and is a direct result of the agents attempting to move towards an optimum position within the structure. This internal movement can be identified by analysing the changes in the inter-agent interactions. This paper discusses two metrics that differ in their approach to identify these changes. The distance metric uses variations in the inter-agent spaces, as used by Navarro et al.~\cite{NIM:09}. The new metric uses the resultant magnitudes from an agents' \textit{inter-agent vectors} that are induced by an agent interacting with its neighbours.

This paper presents a swarm model and then applies the two metrics to this model to present a comparison of the two metrics and uses the new metric to identify a swarm's `state'.
